---
title: "How to use this packaged `drake` workflow"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This package provides the raw data, analysis code, and outputs as well as the computational environment needed to reproduce the project/compendium "drakepkg". The project uses the R package `drake` to define a reproducible processing pipeline linking inputs to outputs/targets similar to `GNU make` (for more information on the `drake` package, see [here](https://ropensci.github.io/drake/)). This vignette describes how to reproduce the analysis, check the analysis pipeline, and inspect analysis steps and outputs.

## Copy the analysis directory structure

```{r}
library(drakepkg)
copy_analysis()
```

After attaching the package, executing the function `copy_analysis()` copies the analysis directory structure  to the current working directory (or an explicitely specified directory). The directory should now contain the following files:

```
.
└── analysis
    ├── data
    │   └── other-iris.xlsx
    ├── manuscript
    │   └── report.html
    └── templates
        └── report.Rmd
```

These files represent all input files required to reproduce the analysis as well as all output files generated in the process. The function further copies the `.drake` directory to the same directory. This hidden directory stores information about the consistency of the analysis pipeline and all intermediate outputs.

## Reproduce the analysis

Reproducing the analysis can be done in a two-step procedure:

1. Executing the function `reproduce_analysis()` copies the analysis directory structure (if it isn't already present) and then runs `drake::make()`. The output provides evidence of reproducibility without actually re-running the analysis. If the analysis is reproducible, the output should look like this:

```{r}
reproduce_analysis()
```

2. To independently re-create the analysis results on ones own computer, one can run `reproduce_analysis()` with the option `re_run = TRUE`. This will delete the copied `.drake` folder and re-run the entire project from scratch, re-creating all relevant intermediate steps and outputs.

```{r}
reproduce_analysis(re_run = TRUE)
```

## Explore the analysis pipeline and results

Executing `get_plan()` returns the underlying `drake` plan used to run the analysis. The returned `tibble` lists all intermediate results (targets), the commands executed to create them, and the dependencies between them.

```{r}
plan <- get_plan()
plan
```

The `drake` package provides  [several ways](https://ropenscilabs.github.io/drake-manual/vis.html) to visualize the project, e.g.

```{r, out.width = "80%"}
config <- drake_config(plan)
vis_drake_graph(config)
```

Furthermore, `drake` provides functions for viewing individual targets (`drake::readd()`) or load them into the current environment (`drake::loadd()`). For example, to view the cleaned data frame, use

```{r}
readd(ready_data) %>% 
  head()
```

or to view the figure included in the report, use

```{r, fig.width = 5, fig.height = 4}
readd(hist)
```

## Cleaning up

Executing `delete_analysis()` removes the `analysis` and `.drake` directories from the working directory (or an explicitely specified directory).

```{r}
delete_analysis()
```
